---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# saapsim

<!-- badges: start -->
<!-- badges: end -->

The goal of saapsim is to provide access to commonly needed functions when working with APSIM (for the Archontoulis Lab). 

## Installation

The development version is on [GitHub](https://github.com/), accessed with

``` {r}
#install.packages("devtools")
#devtools::install_github("vanichols/saapsim")
```

## Example(s)

All functions start with saf_xxx (**s**otris-**a**rchontoulis-**a**psim-**f**unction), so you can easily see a list pop up if you type saf and hit tab. 

You can read in '.out' files and smoosh them into one dataframe with the *saf_readapout* function

```{r example}
#library(saapsim)
#mydir <- "/apsim_results_folder"
#saf_readapout(mydir)
```


You can easily convert corn bushes/acre to dry kg/ha with the *saf_buac_to_kgha_corn* function

```{r example2}
library(saapsim)
saf_buac_to_kgha_corn(210)
```

You can effortlessly figure out what the day-of-year March 21 2000 was with the *saf_

```{r example3}
library(saapsim)
saf_date_to_doy("2000-03-21")
```

